Marlowe: financial contracts on blockchain

### 2018-05-17 tex/paper.tex
moved references in footnotes into bib

%
%
% Title portion. Note the short title for running heads
\title {Marlowe: financial contracts on blockchain\thanks{This work is a part of the Cardano project, and is
supported by IOHK}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Pablo Lamela Seijas\orcidID{0000-0002-1730-1219}\\
\and Simon Thompson\orcidID{0000-0002-2350-301X}}
%
\authorrunning{P. Lamela Seijas and S. Thompson}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of Kent, Canterbury, CT2 7NF, Kent (UK)}
\email{\{pl292,s.j.thompson\}@kent.ac.uk}

@@

This paper explores the design of a domain specific language, Marlowe,\footnote{Marlowe is named after Christopher 
Marlowe, the Elizabethan poet, dramatist and spy, who was born and educated in Canterbury, which is also where our 
university is based. \url{https://en.wikipedia.org/wiki/Christopher_Marlowe}}\footnote{The code for Marlowe is available 
from \url{https://github.com/input-output-hk/scdsl}} targetted at the execution of financial contracts in the style of 
Peyton Jones, Eber and Seward~\cite{PeytonJones:2000} on blockchains. This work is a part of the Cardano project, and is 
supported by IOHK.\footnote{\url{https://iohk.io}}

@@

The \ae{}ternity system~\cite{aeternity} provides multiple languages and VMs:\footnote{As presented by Erik Stenman at 
CODE BEAM SF, March 2018, \url{https://www.youtube.com/watch?v=VXsqvfPIdWg}} the functional language  Sophia (akin to 
Reason) and the Functional Typed Warded Virtual Machine (FTWVM) for safe ``system level programming'', the language 
Varna and the HLM for simple contracts, and a (port of) Solidity and the EVM for compatibility with Ethereum. In a 
similar way, Cardano provides support for IELE~\cite{IELE}, a rational reconstruction of the EVM, and thus for Solidity 
contracts too.

@@

The model does not take time as an observable, but rather it is defined in terms of \haskellinline{BlockNumber} only. 
We could  use ``slot time'' instead: \emph{``We consider a setting where time is divided into discrete units called 
slots. A ledger, described in more detail below, associates with each time slot (at most) one ledger 
block.''}\footnote{\url{https://eprint.iacr.org/2016/889.pdf}}

>>>>

%
%
% Title portion. Note the short title for running heads
\title {Marlowe: financial contracts on blockchain}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Pablo Lamela Seijas\orcidID{0000-0002-1730-1219}\\
\and Simon Thompson\orcidID{0000-0002-2350-301X}}
%
\authorrunning{P. Lamela Seijas and S. Thompson}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{School of Computing, University of Kent, Canterbury, UK}
\email{\{pl292,s.j.thompson\}@kent.ac.uk}

@@

This paper explores the design of a domain specific language, Marlowe,\footnote{Named after Christopher 
Marlowe, the Elizabethan poet, dramatist and spy, who was born and educated in Canterbury,  \url{en.wikipedia.org/wiki/Christopher_Marlowe}}\footnote{Marlowe is available 
from \url{https://github.com/input-output-hk/scdsl}} targetted at the execution of financial contracts in the style of 
Peyton Jones, Eber and Seward~\cite{PeytonJones:2000} on blockchains. This work is a part of the Cardano project, and is 
supported by IOHK,~\url{https://iohk.io}.

@@

The \ae{}ternity system~\cite{aeternity} provides multiple languages and VMs~\cite{Stenman-CODE-BEAM}: the functional language  Sophia (akin to 
Reason) and the Functional Typed Warded Virtual Machine (FTWVM) for safe ``system level programming'', the language 
Varna and the HLM for simple contracts, and a (port of) Solidity and the EVM for compatibility with Ethereum. In a 
similar way, Cardano provides support for IELE~\cite{IELE}, a rational reconstruction of the EVM, and thus for Solidity 
contracts too.

@@

The model does not take time as an observable, but rather it is defined in terms of \haskellinline{BlockNumber} only. 
We could  use ``slot time'' instead: \emph{``We consider a setting where time is divided into discrete units called 
slots. A ledger, described in more detail below, associates with each time slot (at most) one ledger 
block.''}~\cite{Ouroboros}.
